---
title: 'R for Data Science: Exercises for Section Program'
author: ["Garrett Grolemund", "Hadley Wickham"]
output: html_document
---

### Exercises

1.  Read the source code for each of the following three functions, puzzle out
    what they do, and then brainstorm better names.
    
    ```{r}
    f1 <- function(string, prefix) {
      substr(string, 1, nchar(prefix)) == prefix
    }
    f2 <- function(x) {
      if (length(x) <= 1) return(NULL)
      x[-length(x)]
    }
    f3 <- function(x, y) {
      rep(y, length.out = length(x))
    }
    ```
    
1.  Take a function that you've written recently and spend 5 minutes 
    brainstorming a better name for it and its arguments.

1.  Compare and contrast `rnorm()` and `MASS::mvrnorm()`. How could you make
    them more consistent? 
    
1.  Make a case for why `norm_r()`, `norm_d()` etc would be better than
    `rnorm()`, `dnorm()`. Make a case for the opposite.

### Exercises

1.  What's the difference between `if` and `ifelse()`? Carefully read the help
    and construct three examples that illustrate the key differences.

1.  Write a greeting function that says "good morning", "good afternoon",
    or "good evening", depending on the time of day. (Hint: use a time
    argument that defaults to `lubridate::now()`. That will make it 
    easier to test your function.)

1.  How could you use `cut()` to simplify this set of nested if-else statements?

    ```{r, eval = FALSE}
    if (temp <= 0) {
      "freezing"
    } else if (temp <= 10) {
      "cold"
    } else if (temp <= 20) {
      "cool"
    } else if (temp <= 30) {
      "warm"
    } else {
      "hot"
    }
    ```
    
    How would you change the call to `cut()` if I'd used `<` instead of `<=`?
    What is the other chief advantage of `cut()` for this problem? (Hint:
    what happens if you have many values in `temp`?)

1.  What happens if you use `switch()` with numeric values?

1.  What does this `switch()` call do? What happens if `x` is "e"?

    ```{r, eval = FALSE}
    switch(x, 
      a = ,
      b = "ab",
      c = ,
      d = "cd"
    )
    ```
    
    Experiment, then carefully read the documentation. 

### Exercises

1.  What does `commas(letters, collapse = "-")` do? Why?

1.  It'd be nice if you could supply multiple characters to the `pad` argument, 
    e.g. `rule("Title", pad = "-+")`. Why doesn't this currently work? How 
    could you fix it?
    
1.  What does the `trim` argument to `mean()` do? When might you use it?

1.  The default value for the `method` argument to `cor()` is 
    `c("pearson", "kendall", "spearman")`. What does that mean? What 
    value is used by default?

### Exercises

1.  Write for loops to:

    1. Compute the mean of every column in `mtcars`.
    1. Determine the type of each column in `nycflights13::flights`.
    1. Compute the number of unique values in each column of `iris`.
    1. Generate 10 random normals for each of $\mu = -10$, $0$, $10$, and $100$.
    
    Think about the output, sequence, and body __before__ you start writing
    the loop.

1.  Eliminate the for loop in each of the following examples by taking 
    advantage of an existing function that works with vectors:
    
    ```{r, eval = FALSE}
    out <- ""
    for (x in letters) {
      out <- stringr::str_c(out, x)
    }
    
    x <- sample(100)
    sd <- 0
    for (i in seq_along(x)) {
      sd <- sd + (x[i] - mean(x)) ^ 2
    }
    sd <- sqrt(sd / (length(x) - 1))
    
    x <- runif(100)
    out <- vector("numeric", length(x))
    out[1] <- x[1]
    for (i in 2:length(x)) {
      out[i] <- out[i - 1] + x[i]
    }
    ```

1.  Combine your function writing and for loop skills:

    1. Write a for loop that `prints()` the lyrics to the children's song 
       "Alice the camel".

    1. Convert the nursery rhyme "ten in the bed" to a function. Generalise 
       it to any number of people in any sleeping structure.

    1. Convert the song "99 bottles of beer on the wall" to a function.
       Generalise to any number of any vessel containing any liquid on 
       any surface.

1.  It's common to see for loops that don't preallocate the output and instead
    increase the length of a vector at each step:
    
    ```{r, eval = FALSE}
    output <- vector("integer", 0)
    for (i in seq_along(x)) {
      output <- c(output, lengths(x[[i]]))
    }
    output
    ```
    
    How does this affect performance? Design and execute an experiment.

### Exercises

1.  Imagine you have a directory full of csv files that you want to read in.
    You have their paths in a vector, 
    `files <- dir("data/", pattern = "\\.csv$", full.names = TRUE)`, and now
    want to read each one with `read_csv()`. Write the for loop that will 
    load them into a single data frame. 

1.  What happens if you use `for (nm in names(x))` and `x` has no names?
    What if only some of the elements are named? What if the names are
    not unique?

1.  Write a function that prints the mean of each numeric column in a data 
    frame, along with its name. For example, `show_mean(iris)` would print:
    
    ```{r, eval = FALSE}
    show_mean(iris)
    #> Sepal.Length: 5.84
    #> Sepal.Width:  3.06
    #> Petal.Length: 3.76
    #> Petal.Width:  1.20
    ```
    
    (Extra challenge: what function did I use to make sure that the numbers
    lined up nicely, even though the variable names had different lengths?)

1.  What does this code do? How does it work?

    ```{r, eval = FALSE}
    trans <- list( 
      disp = function(x) x * 0.0163871,
      am = function(x) {
        factor(x, labels = c("auto", "manual"))
      }
    )
    for (var in names(trans)) {
      mtcars[[var]] <- trans[[var]](mtcars[[var]])
    }
    ```

### Exercises

1.  Read the documentation for `apply()`. In the 2d case, what two for loops
    does it generalise?

1.  Adapt `col_summary()` so that it only applies to numeric columns
    You might want to start with an `is_numeric()` function that returns
    a logical vector that has a TRUE corresponding to each numeric column.

### Exercises

1.  Write code that uses one of the map functions to:

    1. Compute the mean of every column in `mtcars`.
    1. Determine the type of each column in `nycflights13::flights`.
    1. Compute the number of unique values in each column of `iris`.
    1. Generate 10 random normals for each of $\mu = -10$, $0$, $10$, and $100$.

1.  How can you create a single vector that for each column in a data frame
    indicates whether or not it's a factor?

1.  What happens when you use the map functions on vectors that aren't lists?
    What does `map(1:5, runif)` do? Why?
    
1.  What does `map(-2:2, rnorm, n = 5)` do? Why?
    What does `map_dbl(-2:2, rnorm, n = 5)` do? Why?

1.  Rewrite `map(x, function(df) lm(mpg ~ wt, data = df))` to eliminate the 
    anonymous function. 

### Exercises

1.  Implement your own version of `every()` using a for loop. Compare it with
    `purrr::every()`. What does purrr's version do that your version doesn't?

1.  Create an enhanced `col_sum()` that applies a summary function to every
    numeric column in a data frame.

1.  A possible base R equivalent of `col_sum()` is:

    ```{r}
    col_sum3 <- function(df, f) {
      is_num <- sapply(df, is.numeric)
      df_num <- df[, is_num]

      sapply(df_num, f)
    }
    ```
    
    But it has a number of bugs as illustrated with the following inputs:
    
    ```{r, eval = FALSE}
    df <- tibble::tibble(
      x = 1:3, 
      y = 3:1,
      z = c("a", "b", "c")
    )
    # OK
    col_sum3(df, mean)
    # Has problems: don't always return numeric vector
    col_sum3(df[1:2], mean)
    col_sum3(df[1], mean)
    col_sum3(df[0], mean)
    ```
    
    What causes the bugs?
