\documentclass[]{article}
\usepackage[margin=1in]{geometry}
\newcommand*{\authorfont}{\fontfamily{phv}\selectfont}
\usepackage{lmodern}
\usepackage{abstract}
\renewcommand{\abstractname}{}    % clear the title
\renewcommand{\absnamepos}{empty} % originally center
\newcommand{\blankline}{\quad\pagebreak[2]}

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}} 
\usepackage{longtable,booktabs}

\usepackage{parskip}
\usepackage{titlesec}
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{6pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{6pt plus 2pt minus 2pt}

\titleformat*{\subsubsection}{\normalsize\itshape}

\usepackage{titling}
\setlength{\droptitle}{-.25cm}

%\setlength{\parindent}{0pt}
%\setlength{\parskip}{6pt plus 2pt minus 1pt}
%\setlength{\emergencystretch}{3em}  % prevent overfull lines 

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{lastpage}
\renewcommand{\headrulewidth}{0.3pt}
\renewcommand{\footrulewidth}{0.0pt} 
\lhead{}
\chead{}
\rhead{\footnotesize POLI 7450: Computational Methods for Comparative Research -- Spring 2019}
\lfoot{}
\cfoot{\small \thepage/\pageref*{LastPage}}
\rfoot{}

\fancypagestyle{firststyle}
{
\renewcommand{\headrulewidth}{0pt}%
   \fancyhf{}
   \fancyfoot[C]{\small \thepage/\pageref*{LastPage}}
}

%\def\labelitemi{--}
%\usepackage{enumitem}
%\setitemize[0]{leftmargin=25pt}
%\setenumerate[0]{leftmargin=25pt}




\makeatletter
\@ifpackageloaded{hyperref}{}{%
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
}
\@ifpackageloaded{color}{
    \PassOptionsToPackage{usenames,dvipsnames}{color}
}{%
    \usepackage[usenames,dvipsnames]{color}
}
\makeatother
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={ ()},
             pdfkeywords = {},  
            pdftitle={POLI 7450: Computational Methods for Comparative Research},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls


\setcounter{secnumdepth}{0}

\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}




\usepackage{setspace}

\title{POLI 7450: Computational Methods for Comparative Research}
\author{Prof.~Frederick Solt}
\date{Spring 2019}


\begin{document}  

		\maketitle
		
	
		\thispagestyle{firststyle}

%	\thispagestyle{empty}


	\noindent \begin{tabular*}{\textwidth}{ @{\extracolsep{\fill}} lr @{\extracolsep{\fill}}}


E-mail: \texttt{\href{mailto:frederick-solt@uiowa.edu}{\nolinkurl{frederick-solt@uiowa.edu}}} & Web: \href{http://cmcr-class.github.io}{\tt cmcr-class.github.io}\\
Office Hours: TTh 9:30 to 11:00 am and by appointment  &  Class Hours: T 11:00 am to 1:50 pm\\
Office: 324 Schaeffer Hall  & Class Room: 103 Schaeffer Hall\\
	&  \\
	\hline
	\end{tabular*}
	
\vspace{2mm}
	


\hypertarget{overview}{%
\section{Overview}\label{overview}}

In this course, you will learn to identify common methodological issues
encountered in quantitative comparative research and to address them
using computational techniques. Topics covered include data wrangling,
exploration, and analysis (i.e., `data science'); Bayesian estimation of
latent variables such as democracy, judicial independence, and respect
for human rights across countries and over time; and computational
approaches to the study to the dynamics of public opinion both within
and across countries. This course is cross-listed in Comparative
Politics and Methodology; it may be used to meet requirements in either
subfield (but not both).

\hypertarget{course-requirements}{%
\section{Course Requirements}\label{course-requirements}}

Your grade will be based on class participation (20\%), assignments
(10\%), an exam (25\%), a research presentation (20\%), and a research
paper (25\%). The following grades may be assigned at the end of the
class: A+, A, A-, B+, B, B-, C+, C, C-, D+, D, D-, F.

\hypertarget{class-participation}{%
\subsection{Class Participation}\label{class-participation}}

By this point in your career this should really go without saying, but
here it is anyway: you can't learn in a class if you don't show up. You
should attend every meeting having completed the readings and
assignments, that is, you should be ready to discuss use cases, ask good
questions, and share any difficulties you've encountered.

We will also be using
\href{https://github.com/cmcr-class/Discussion/issues}{the Issues tab of
a dedicated GitHub repository} to continue our discussions outside of
class. To start a new thread, create a new issue. If you want to be sure
to get the attention of someone in particular, use their GitHub
handle---mine is \texttt{@fsolt}---to tag them in your post: GitHub
sends an email to people when they are tagged.

\hypertarget{assignments}{%
\subsection{Assignments}\label{assignments}}

To practice your new skills, you will have regular assignments. Some
will be completed through GitHub in a private repository for each
student (besides you, only I will have access to your homework repo).
Others will be DataCamp short courses. Others still will simply be
readings that I want you to be sure to step through the embedded code.
All will be graded on a pass (that is, substantially completed)/fail
basis.

\hypertarget{exam}{%
\subsection{Exam}\label{exam}}

The exam will be available for your to take anytime after class on March
12 until the start of class on March 26. It will be open-note,
open-interwebs---you know, just like
\href{http://www.theallium.com/engineering/computer-programming-to-be-officially-renamed-googling-stackoverflow/}{IRL}.
Don't click the GitHub invitation link until you have three hours to
spend completing the exam.

\hypertarget{research-paper}{%
\subsection{Research Paper}\label{research-paper}}

The research paper for this course is more straightforward than the
usual: the assignment is ``simply'' to write a fully reproducible
version of a quantitative research paper you prepared for another class.
Ideally the paper will be for a class you are taking this semester, so
that you use best practices as you go; you will need to confirm with the
instructor of that course that this is acceptable to her or him.
Rewriting a promising paper from past coursework will also be fine,
though. If you're stuck for an appropriate paper, talk to me and we will
work it out.

For your paper, you will:

\begin{itemize}
\tightlist
\item
  write using RMarkdown (or \texttt{knitr}) with interspersed \textsf{R}
  code and text,
\item
  begin with raw data collection,
\item
  include all steps of data cleaning and analysis,
\item
  present figures rather than tables,
\item
  use Bib\TeX for citations,
\item
  automatically generate PDF, html, and
  (\raisebox{0.7ex}{ee}\raisebox{0.3ex}{e}w\raisebox{-0.3ex}{ww}\raisebox{-0.7ex}{w}!)
  Word versions,
\item
  do your work in a GitHub repository,
\item
  submit a link to that repo.
\end{itemize}

Papers are due the last day of exam week, Friday, May 10, before
midnight.

\hypertarget{research-presentation}{%
\subsection{Research Presentation}\label{research-presentation}}

In our last class meeting, you will give a presentation based on your
research paper to the class as if at an academic conference. You will
speak for 12 to 15 minutes. You will have slides; these slides will not
be filled with blocks of text. You will use plots, not tables, to
present results. You will rock this.

\pagebreak

\hypertarget{course-schedule}{%
\section{Course Schedule}\label{course-schedule}}

\hypertarget{week-1-january-15-introduction-to-the-course}{%
\subsection{Week 1, January 15: Introduction to the
Course}\label{week-1-january-15-introduction-to-the-course}}

\emph{Assignment}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \href{http://happygitwithr.com}{Bryan, Jennifer. 2016.
  \textit{Happy Git and GitHub for the UseR.} Chapters 1-16.} Read this
  carefully and follow its instructions to get set up with \textsf{R},
  RStudio, Git, and GitHub on your laptop before we meet.
\end{enumerate}

\hypertarget{week-2-january-22-the-replication-crisis-and-reproducibility}{%
\subsection{Week 2, January 22: The Replication Crisis and
Reproducibility}\label{week-2-january-22-the-replication-crisis-and-reproducibility}}

\emph{Readings}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \href{http://fivethirtyeight.com/features/how-two-grad-students-uncovered-michael-lacour-fraud-and-a-way-to-change-opinions-on-transgender-rights/}{Aschwanden,
  Christie, and Maggie Koerth-Baker. 2016. ``How Two Grad Students
  Uncovered an Apparent Fraud---and a Way to Change Opinions on
  Transgender Rights.'' \emph{FiveThirtyEight}, April 7}, and
  \href{http://blogs.lse.ac.uk/impactofsocialsciences/2013/04/24/reinhart-rogoff-revisited-why-we-need-open-data-in-economics/}{Dimitrova,
  Velichka. 2013. ``Reinhart-Rogoff Revisited: Coding Errors
  Happen---Key Problem Was in Not Making the Data Openly Available from
  the Start.'' \emph{LSE: The Impact Blog}, April 24.}
\item
  \href{http://journals.cambridge.org/action/displayAbstract?fromPage=online\&aid=9911378\&fulltextType=LT\&fileId=S2049847015000448}{Data
  Access and Research Transparency (DA-RT): A Joint Statement by
  Political Science Journal Editors.}
\item
  \href{https://ajps.org/ajps-replication-policy/}{\emph{AJPS}
  Replication and Verification Policy} and
  \href{https://ajpsblogging.files.wordpress.com/2015/03/ajps-guide-for-replic-materials-1-0.pdf}{\emph{American
  Journal of Political Science} Guidelines for Preparing Replication
  Files.}
\item
  \href{http://www.stat.columbia.edu/~gelman/research/unpublished/p_hacking.pdf}{Gelman,
  Andrew, and Eric Loken. 2013. ``The Garden of Forking Paths: Why
  Multiple Comparisons Can Be a Problem, Even When There Is No `Fishing
  Expedition' or `\emph{p}-Hacking' and the Research Hypothesis Was
  Posited Ahead of Time.''}
\item
  \href{http://www.pnas.org.proxy.lib.uiowa.edu/content/112/6/1645}{Leek,
  Jeffrey T., and Roger D. Peng. 2015. ``Opinion: Reproducibile Research
  Can Still Be Wrong: Adopting a Prevention Approach.''
  \emph{Proceedings of the National Academy of Sciences}
  112(6):1645-1646} and
  \href{http://biorxiv.org/content/biorxiv/early/2016/07/29/066803.full.pdf}{Patil,
  Prasad, Roger D. Peng, and Jeffrey T. Leek. 2016. ``A Statistical
  Definition for Reproducibility and Replicability.'' \emph{bioRxiv},
  July 29.}
\item
  \href{https://www-journals-uchicago-edu.proxy.lib.uiowa.edu/doi/pdfplus/10.1086/690971}{Solt,
  Frederick, Yue Hu, Kevan Hudson, Jungmin Song, and Dong `Erico' Yu.
  2017. ``Economic Inequality and Class Consciousness.'' \emph{Journal
  of Politics} 79(3):1079-1083.}
\end{enumerate}

\emph{Assignments}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \href{https://happygitwithr.com/rmd-test-drive.html}{Bryan, Jennifer.
  2016. \emph{Happy Git and GitHub for the UseR.} Chapter 18.}
\end{enumerate}

\hypertarget{week-3-january-29-settling-in-with}{%
\subsection{\texorpdfstring{Week 3, January 29: Settling In with
\textsf{R}}{Week 3, January 29: Settling In with }}\label{week-3-january-29-settling-in-with}}

\emph{Readings}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \href{https://moderndive.com/index.html}{Ismay, Chester, and Albert Y.
  Kim. 2018. \emph{Modern Dive: An Introduction to Statistical and Data
  Sciences via R}, Chapters 1 and 2.}
\item
  \href{https://socviz.co/}{Healy, Kieran. 2018. \emph{Data
  Visualization: A Practical Introduction}, Preface and Chapter 2.} Some
  overlap with Ismay and Kim, but that will probably be useful to you at
  this point.
\item
  \href{https://fsolt.org/blog/2018/08/15/switch-to-r.html}{Solt,
  Frederick. 2018. ``How to Switch Your Workflow from Stata to R, One
  Bit at a Time.''}
\end{enumerate}

\emph{Assignments}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Use the interactive \texttt{swirl} package (``Learn \textsf{R} in
  \textsf{R}'') to learn (or review) some \textsf{R} basics. First, run
  the following code to get to the \texttt{swirl} interface:
\end{enumerate}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{install.packages}\NormalTok{(}\StringTok{"swirl"}\NormalTok{)}
\KeywordTok{library}\NormalTok{(}\StringTok{"swirl"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{quote}
Then follow the prompts to the course
\texttt{1:~R Programming:~The basics of programming in R} and complete
lessons 1 through 9. (When it asks whether you want Coursera credit,
just say no.)
\end{quote}

\pagebreak

\hypertarget{week-4-february-5-visualization}{%
\subsection{Week 4, February 5:
Visualization}\label{week-4-february-5-visualization}}

\emph{Readings}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \href{http://dx.doi.org.proxy.lib.uiowa.edu/10.1017/S1537592707072209}{Kastellec,
  Jonathan P. and Eduardo L. Leoni. 2007. ``Using Graphs Instead of
  Tables in Political Science.'' \emph{Perspectives on Politics}
  5(4):755--771.}
\item
  \href{https://moderndive.com/3-viz.html}{Ismay, Chester, and Albert Y.
  Kim. 2018. \emph{Modern Dive: An Introduction to Statistical and Data
  Sciences via R}, Chapter 3.}
\item
  \href{https://cran.r-project.org/web/packages/dotwhisker/vignettes/dotwhisker-vignette.html}{Solt,
  Frederick, and Yue Hu. 2015. ``\texttt{dotwhisker}: Dot-and-Whisker
  Plots of Regression Results.'' Available at The Comprehensive R
  Archive Network (CRAN).}, and especially
  \href{https://cran.r-project.org/web/packages/dotwhisker/vignettes/kl2007_examples.html}{how
  to remake the examples from Kastellec and Leoni (2007) using
  \texttt{dotwhisker}}.
\end{enumerate}

\emph{Assignments}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \href{https://socviz.co/lookatdata.html}{Healy, Kieran. 2018.
  \emph{Data Visualization: A Practical Introduction}, Chapters 1 and
  3.}
\end{enumerate}

\emph{Recommended}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \href{http://www.cookbook-r.com/Graphs/}{Chang, Winston. 2013.
  \emph{Cookbook for R}, Chapter 8: Graphs.} Skim a couple sections to
  get a feel for this as a reference. I myself refer to it all. the.
  time.
\item
  \href{https://serialmentor.com/dataviz/visualizing-uncertainty.html}{Wilke,
  Claus O. 2019. ``Visualizing Uncertainty,'' \emph{Fundamentals of Data
  Visualization}}
\end{enumerate}

\hypertarget{week-5-february-12-wranglin-data}{%
\subsection{Week 5, February 12: Wranglin'
Data}\label{week-5-february-12-wranglin-data}}

\emph{Readings}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \href{https://cran.r-project.org/web/packages/rio/vignettes/rio.html}{Leeper,
  Thomas J. 2016. ``\texttt{rio}: A Swiss-Army Knife for Data I/O.
  Import, Export, and Convert Data Files.''}
\item
  \href{https://moderndive.com/4-tidy.html}{Ismay, Chester, and Albert
  Y. Kim. 2018. \emph{Modern Dive: An Introduction to Statistical and
  Data Sciences via R}, Chapters 4 and 5.}
\item
  \href{https://socviz.co/groupfacettx.html}{Healy, Kieran. 2018.
  \emph{Data Visualization: A Practical Introduction}, Chapters 4 and
  5.}
\end{enumerate}

\emph{Assignment}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \href{https://www.datacamp.com/courses/introduction-to-the-tidyverse}{Robinson,
  David. Datacamp Course: Introduction to the Tidyverse.}
\end{enumerate}

\emph{Recommended}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \href{https://github.com/rstudio/cheatsheets/raw/master/data-transformation.pdf}{RStudio's
  Data Transformation Cheat Sheet.} I had
  \href{https://www.rstudio.com/wp-content/uploads/2015/02/data-wrangling-cheatsheet.pdf}{the
  old version} open on a dedicated desktop on my computer for at least a
  year---maybe two!---before I finally stopped looking at it like twenty
  times a day. Lots of people print it out; I've even heard of people
  laminating it.
\end{enumerate}

\hypertarget{week-6-february-19-wranglin-data-ii-working-with-text}{%
\subsection{Week 6, February 19: Wranglin' Data II, Working with
Text}\label{week-6-february-19-wranglin-data-ii-working-with-text}}

\emph{Assignment}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \href{https://www.datacamp.com/courses/string-manipulation-in-r-with-stringr}{Wickham,
  Charlotte. Datacamp Course: String Manipulation in R with stringr.}
\end{enumerate}

\emph{Recommended}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \href{https://github.com/rstudio/cheatsheets/raw/master/strings.pdf}{RStudio's
  Work with Strings Cheat Sheet.}
\item
  \href{https://www.tidytextmining.com/index.html}{Silge, Julia, and
  David Robinson. 2018. \emph{Text Mining with R: A Tidy Approach}.}
\end{enumerate}

\pagebreak

\hypertarget{week-7-february-26-scraping-and-managing-data}{%
\subsection{Week 7, February 26: Scraping (and Managing)
Data}\label{week-7-february-26-scraping-and-managing-data}}

\emph{Readings}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \href{https://rawgit.com/Reproducible-Science-Curriculum/rr-organization1/master/organization-01-slides.html}{Bryan,
  Jennifer. ``Organization I: File Naming.''}
\item
  \href{https://politicalsciencereplication.wordpress.com/2015/03/16/good-practice-in-data-collection-and-storing/}{Janz,
  Nicole. 2015. ``Good Practice in Data Collection and Storing.''
  \emph{Political Science Replication}, March 16.}
\item
  \href{http://varianceexplained.org/r/trump-tweets/}{Robinson, David.
  2016. ``Text Analysis of Trump's Tweets Confirms He Writes Only the
  (Angrier) Android Half.'' \emph{Variance Explained}, August 9.}
\item
  \href{https://cran.r-project.org/web/packages/gesis/vignettes/gesis.html}{Persson,
  Eric. 2017. \texttt{gesis}: R Client for GESIS Data Catalogue (DBK). R
  package version 0.2.1};
  \href{https://cran.r-project.org/web/packages/icpsrdata/vignettes/icpsrdata-vignette.html}{Solt,
  Frederick and Kellen Gracey. 2016. \texttt{icpsrdata}: Reproducible
  Data Retrieval from the ICPSR Archive. R package version 0.3.0.}; and
  \href{https://cran.r-project.org/web/packages/ropercenter/vignettes/ropercenter-vignette.html}{Frederick
  Solt. 2018. \texttt{ropercenter}: Reproducible Data Retrieval from the
  Roper Center Data Archive. R package version 0.2.0.}
\item
  \href{https://blog.rstudio.org/2014/11/24/rvest-easy-web-scraping-with-r/}{RStudio.
  2014. ``\texttt{rvest}: Easy Web Scraping with R.'' \emph{RStudio
  Blog}, November 24.}
\end{enumerate}

\hypertarget{week-8-march-5-multilevel-models-of-multiple-surveys-i}{%
\subsection{Week 8, March 5: Multilevel Models of Multiple Surveys
I}\label{week-8-march-5-multilevel-models-of-multiple-surveys-i}}

\emph{Readings}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \href{http://www.jstor.org.proxy.lib.uiowa.edu/stable/25193796}{Solt,
  Frederick. 2008. ``Economic Inequality and Democratic Political
  Engagement.'' \emph{American Journal of Political Science}
  52(1):48-60.}
\item
  \href{https://www-journals-uchicago-edu.proxy.lib.uiowa.edu/doi/pdfplus/10.1086/690971}{Solt,
  Frederick, Yue Hu, Kevan Hudson, Jungmin Song, and Dong `Erico' Yu.
  2017. ``Economic Inequality and Class Consciousness.'' \emph{Journal
  of Politics} 79(3):1079-1083.} Yes, \emph{again}, but this time, work
  through
  \href{https://github.com/fsolt/class_consciousness/blob/master/paper/class_consciousness.Rnw}{the
  replication code}.
\end{enumerate}

\hypertarget{week-9-march-12-multilevel-models-of-multiple-surveys-ii}{%
\subsection{Week 9, March 12: Multilevel Models of Multiple Surveys
II}\label{week-9-march-12-multilevel-models-of-multiple-surveys-ii}}

\emph{Readings}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \href{http://mc-stan.org/rstanarm/articles/rstanarm.html}{Gabry,
  Jonah, and Ben Goodrich. 2018. ``How to Use the \texttt{rstanarm}
  Package.''}
\end{enumerate}

\hypertarget{week-10-march-19-spring-break}{%
\subsection{Week 10, March 19: Spring
Break}\label{week-10-march-19-spring-break}}

\hypertarget{week-11-march-26-crowdsourcing-cross-national-data}{%
\subsection{Week 11, March 26: Crowdsourcing Cross-National
Data}\label{week-11-march-26-crowdsourcing-cross-national-data}}

\emph{Readings}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \href{http://dx.doi.org.proxy.lib.uiowa.edu/10.1017/S0003055416000058}{Benoit,
  Kenneth, Drew Conway, Benjamin E. Lauderdale, Michael Laver, and Slava
  Mikhaylov. 2016. ``Crowd-sourced Text Analysis: Reproducible and Agile
  Production of Political Data.'' \emph{American Political Science
  Review} 110(2):278-295.}
\end{enumerate}

\emph{Assignment}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Take-home exam: open book, open notes, open internet. Don't click the
  GitHub invitation link until you have three hours to spend completing
  the exam.
\end{enumerate}

\hypertarget{week-12-april-2-estimating-cross-national-latent-variables}{%
\subsection{Week 12, April 2: Estimating Cross-National Latent
Variables}\label{week-12-april-2-estimating-cross-national-latent-variables}}

\emph{Readings}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \href{http://pan.oxfordjournals.org.proxy.lib.uiowa.edu/content/18/4/426}{Pemstein,
  Daniel, Stephen A. Meserve, and James Melton. 2010. ``Democratic
  Compromise: A Latent Variable Analysis of Ten Measures of Regime
  Type.'' \emph{Political Analysis} 18(4):426-449.}
\item
  \href{http://dx.doi.org.proxy.lib.uiowa.edu/10.1017/S0003055414000070}{Fariss,
  Christopher J. 2014. ``Respect for Human Rights Has Improved Over
  Time: Modeling the Changing Standard of Accountability.''
  \emph{American Political Science Review} 108(2):297-318.}
\item
  \href{http://www.journals.uchicago.edu.proxy.lib.uiowa.edu/doi/10.1086/682150}{Linzer,
  Drew A., and Jeffrey K. Staton. 2015. ``A Global Measure of Judicial
  Independence, 1948-2012.'' \emph{Journal of Law and Courts}
  3(2):223-256.}
\item
  Solt, Frederick. 2019. ``Measuring Income Inequality Across Countries
  and Over Time: The Standardized World Income Inequality Database''.
\end{enumerate}

\pagebreak

\hypertarget{week-13-april-9-analysis-with-cross-national-latent-variables}{%
\subsection{Week 13, April 9: Analysis with Cross-National Latent
Variables}\label{week-13-april-9-analysis-with-cross-national-latent-variables}}

\emph{Readings}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \href{http://rap.sagepub.com/content/2/3/2053168015605343}{Crabtree,
  Charles D., and Fariss, Christopher J. 2015. ``Uncovering Patterns
  Among Latent Variables: Human Rights and De Facto Judicial
  Independence.'' \emph{Research \& Politics} 2(3):1-9.}
\end{enumerate}

\emph{Assignment}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \href{http://www.unified-democracy-scores.org/example.html}{Pemstein,
  Meserve, and Melton provide an example} of how use Stata to employ
  their Unified Democracy Scores in research. Replicate their example
  but show instead how to use the UDS in \textsf{R}. You \emph{might}
  find \href{http://dx.doi.org/10.7910/DVN/LVYOKM}{Crabtree and Fariss's
  reproducibility materials} to be a bit helpful, but you should of
  course use the \texttt{tidyverse} methods we've learned this semester.
\end{enumerate}

\hypertarget{week-14-april-16-public-opinion-in-one-country-as-a-latent-variable}{%
\subsection{Week 14, April 16: Public Opinion in One Country as a Latent
Variable}\label{week-14-april-16-public-opinion-in-one-country-as-a-latent-variable}}

\emph{Readings}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \href{http://pan.oxfordjournals.org.proxy.lib.uiowa.edu/content/22/1/115.abstract}{McGann,
  Anthony J. 2014. ``Estimating the Political Center from Aggregate
  Data: An Item Response Theory Alternative to the Stimson Dyad Ratios
  Algorithm.'' \emph{Political Analysis} 22(1):115-129.}
\end{enumerate}

\hypertarget{week-15-april-23-public-opinion-as-a-cross-national-latent-variable}{%
\subsection{Week 15, April 23: Public Opinion as a Cross-National Latent
Variable}\label{week-15-april-23-public-opinion-as-a-cross-national-latent-variable}}

\emph{Readings}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  TBA
\end{enumerate}

\hypertarget{week-16-april-30-presentations}{%
\subsection{Week 16, April 30:
Presentations}\label{week-16-april-30-presentations}}

\emph{Readings}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \href{https://huber.research.yale.edu/materials/HowToPresentAtConferences.pdf}{Huber,
  Gregory. ``How to Present Your Work at Conferences.''}
\end{enumerate}

\emph{Recommended}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \href{https://speakerdeck.com/mseckington/the-art-of-talk-design}{Secklington,
  Melinda. 2018. ``The Art of Talk Design.''}
\item
  \href{https://speakerdeck.com/mseckington/the-art-of-slide-design}{Secklington,
  Melinda. 2017. ``The Art of Slide Design.''}
\end{enumerate}

\pagebreak

\hypertarget{further-course-information}{%
\section{Further Course Information}\label{further-course-information}}

\hypertarget{administrative-home}{%
\subsubsection{Administrative Home}\label{administrative-home}}

The College of Liberal Arts and Sciences (CLAS) is the administrative
home of this course and governs its add/drop deadlines, the
second-grade-only option, and other policies. These policies vary by
college. See the \href{http://clas.uiowa.edu/students/handbook}{CLAS
\emph{Student Academic Handbook}}.

\hypertarget{electronic-communication}{%
\subsubsection{Electronic
Communication}\label{electronic-communication}}

Students are responsible for official correspondences sent to their UI
email address (uiowa.edu) and must use this address for all
communication within UI
(\href{http://www.uiowa.edu/~our/opmanual/iii/15.htm\#152}{\emph{Operations
Manual}}, III.15.2. Scroll down to k.11.)

\hypertarget{accommodations-for-disabilities}{%
\subsubsection{Accommodations for
Disabilities}\label{accommodations-for-disabilities}}

UI is committed to an educational experience that is accessible to all
students. A student may request academic accommodations for a disability
(such as mental health, attention, learning, vision, and physical or
health-related condition) by registering with Student Disability
Services (SDS). The student should then discuss accommodations with the
course instructor. See \url{https://sds.studentlife.uiowa.edu/} for more
information.

\hypertarget{nondiscrimination-in-the-classroom}{%
\subsubsection{Nondiscrimination in the
Classroom}\label{nondiscrimination-in-the-classroom}}

UI is committed to making the classroom a respectful and inclusive space
for all people irrespective of their gender, sexual, racial, religious
or other identities. Toward this goal, students are invited to
optionally share their preferred names and pronouns with their
instructors and classmates. The University of Iowa prohibits
discrimination and harassment against individuals on the basis of race,
class, gender, sexual orientation, national origin, and other identity
categories set forth in the University's Human Rights policy. For more
information, contact the Office of Equal Opportunity and Diversity. See
\textless{}diversity.uiowa.edu\textgreater{} for more information.

\hypertarget{academic-honesty}{%
\subsubsection{Academic Honesty}\label{academic-honesty}}

All CLAS students or students taking classes offered by CLAS have, in
essence, agreed to the College's
\href{https://clas.uiowa.edu/students/handbook/academic-fraud-honor-code}{Code
of Academic Honesty}. Misconduct is reported to the College, resulting
in suspension or other sanctions, with sanctions communicated with the
student through the UI email address See
\url{https://clas.uiowa.edu/students/handbook/academic-fraud-honor-code}
for more information.

\hypertarget{clas-final-examination-policies}{%
\subsubsection{CLAS Final Examination
Policies}\label{clas-final-examination-policies}}

The final exam schedule for each semester is announced around the fifth
week of classes; students are responsible for knowing the date, time,
and place of a final exam. Students should not make travel plans until
knowing this final exam information. No exams of any kind are allowed
the week before finals. See
\url{https://clas.uiowa.edu/faculty/teaching-policies-resources-examination-policies}
for more information.

\hypertarget{making-a-complaint}{%
\subsubsection{Making a Complaint}\label{making-a-complaint}}

Students with a suggestion or complaint should first visit the
instructor, \href{mailto:frederick-solt@uiowa.edu}{Professor Solt}, and
then the departmental DEO, \href{mailto:brian-lai@uiowa.edu}{Dr.~Brian
Lai} (Office: 343 SH). Students may then bring the concern to CLAS See
\url{https://clas.uiowa.edu/students/handbook/student-rights-responsibilities}
for more information.

\hypertarget{understanding-sexual-harassment}{%
\subsubsection{Understanding Sexual
Harassment}\label{understanding-sexual-harassment}}

Sexual harassment subverts the mission of the University and threatens
the well-being of students, faculty, and staff. All members of the UI
community must uphold the UI mission and contribute to a safe
environment that enhances learning. Incidents of sexual harassment must
be reported immediately. For assistance, definitions, and the full
University policy, see \url{https://osmrc.uiowa.edu/}.

\hypertarget{reacting-safely-to-severe-weather}{%
\subsubsection{Reacting Safely to Severe
Weather}\label{reacting-safely-to-severe-weather}}

In severe weather, class members should seek appropriate shelter
immediately, leaving the classroom if necessary. The class will continue
if possible when the event is over. For more information on Hawk Alert
and the siren warning system, visit the
\href{https://police.uiowa.edu/emergency-communications}{Department of
Public Safety website}.

\hypertarget{student-resources}{%
\subsubsection{Student Resources}\label{student-resources}}

I encourage interested students to make use of
\href{http://www.uiowa.edu/~writingc/}{the Writing Center} and
\href{https://tippie.uiowa.edu/clas/scheduler/logon.aspx?}{the Speaking
Center}.




\end{document}

\makeatletter
\def\@maketitle{%
  \newpage
%  \null
%  \vskip 2em%
%  \begin{center}%
  \let \footnote \thanks
    {\fontsize{18}{20}\selectfont\raggedright  \setlength{\parindent}{0pt} \@title \par}%
}
%\fi
\makeatother
